\textbf{Department Invited Speakers Do Not Reflect Trainee Diversity}

### 2019-09-24 submission/manuscript.tex
revise discussion, add references

@@

@@

Each academic year, each faculty member in the Department of
Microbiology and Immunology at the University of Michigan has the
opportunity to invite one speaker per year for a weekly seminar series.
Some of these seminar slots are dedicated to named lectureships, which
are decided by committee, and three trainee-invited speakers. We
analyzed the demographics of invited speakers and faculty hosts for five
academic years (Fall 2014 - Spring 2019), and compared them to the
current trainees when the data were analyzed (Spring 2019). Each speaker
was only counted once and those listed as departmental faculty members
or as a ``host'' at any point could not also be considered ``invited
speakers''. The list of faculty hosts was used as a proxy for faculty
demographics since as hosts, these faculty members are visible
representatives of the department. The trainee lists were obtained from
department listservs that included masters students, doctoral students,
and post-doctoral fellows.

This is a retrospective study, so individuals were not asked for their
identities. Instead we hand-coded proxy demographics using personal
knowledge, photos, and CVs. The presenting gender of each individual was
assigned using a binary system (man/woman). Due to the low number of
individuals in the study, race/ethnicity demographics were split in
three groups: Caucasian, Historically Under-represented Minority (HURM),
and Non-Caucasian/Non-HURM (NCNH), each with a binary (yes/no)
possibilty. Caucasian was assigned using the current U.S. Census
definition where those of Middle Eastern, European, and Russian descent
are included. HURM individuals were restricted to those with
African-American, Indigenous, Alaskan/Hawaian Native, Latinx and/or
Hispanic heritage. All others were placed into the NCNH group. We
recognize that our proxy demographics are a limitation of the analysis
and want to acknowledge that the presenting gender may not reflect the
gender(s) that an individual identifies as. We also want to acknowledge
that there are many other identities that are not captured in this
limited analysis.

@@

The more prestigous invited speaker lectureships were also dominated by
caucasian scientists, who comprised 81.48\% of those awarded (Fig. 1C).
HURM and NCNH scientists were awarded 3 and 2 lectureships,
respectively. Because the intersection of identities can compound biases
and outcomes, we further examined the lectureships by gender and
race/ethnicity status. Caucasian men and women accounted for 44.44\% and
37.04\% of the lectureships, respectively. Just 18.52\% of lectureships
were held by non-Caucasian men while none were held by non-Caucasian
women (Fig. 1D).

@@

Several papers have investigated the representation of women at
scientific conferences, however, we have only identified one that
focused on invited speakers at universities (23). In their study,
Nittrouer et al, examined 3,652 talks at 50 U.S. institutions in 2013 -
2014 and found that women faculty are less likely to be invited
speakers, despite similar acceptance rates. These results suggest that
women faculty are less often invited as speakers, a decision that may be
negatively impacted by assumptions about competency and dedication. The
dedication of women who have children to their work is perceived to be
less than that of their colleagues, i.e., men who also have children.
The perceived prioritization and commitments of women to family over
work may cause faculty to doubt their acceptance of a speaking
invitation (despite the prestigious nature of these invitations and
evidence to the contrary)({\textbf{???}}, 23). As a result, the faculty
member invites a different colleague who they feel is more likely to
agree (and is a man). Departments have different processes and criteria
for selecting invited speakers, but it is a matter of pride to bring the
best scientists possible. It may be that the definition of ``best''
poses a problem to women, who need three-times as many publications as
their men colleges to be considered equally competent. Some departments
only invite tenured faculty, which severely limits the number of
potential women speakers. Another scenario is that pre-tenure faculty
members invite prestigious, tenured faculty in their field to network
and secure letters for their own tenure package. The increased burden of
women to prove competency decreases their likelihood to be considered
for either tenure or as possible source of tenure letters.

The desire to invite the ``best'' scientist to these seminar series also
poses a problem for HURM and NCNH scientists. A large portion of the
NCNH cohort in our sample are Asian/Asian American individuals. Although
Asian scientists are well-represented in the US scientific workforce,
they face significant bias and barriers to inclusion in society and
academia (24, 25). Both men and women who identify as HURM and Asian
reported having to work harder than white men to be perceived as
legitimate scholars (26). This expectation of higher productivity may
result in fewer HURM and NCNH individuals being invited as seminar
speakers. This is particularly striking in the low number of NCNH
individuals in the more prestigious lectureships of our sample despite
the higher employment rate of Asian scientists.

While HURM and NCNH share some experiences, differences including
varying rates of hiring and tenure promotion mean unique considerations
are important for inclusion of each group
(\url{doi:10.1001/jama.284.9.1085}). For instance, the proportion of
HURM faculty at the Assistant and Associate Professor level is currently
higher than the Full Professor level so it will be difficult to increase
speaker diversity if early-career researchers are not being considered
(27). Increased performance expectations and patterns of exclusions are
consistent themes in studies characterizing the HURM faculty experience
(28, 29). Therefore, inclusion of HURM faculty in seminar series is
likely essential to increasing the number of HURM Associate and Full
Professors. More significantly, a major barrier to inclusion of HURM
faculty at similar proportions to HURM trainees is the low transition
rate of scientists from HURM backgrounds to faculty positions and the
associated low proportion of HURM faculty (30). Even when HURM speaker
rates match the proportion of HURM faculty employment, HURM trainees
will be represented at a significantly higher proportion. Inclusion of
HURM faculty in these seminarseries is just one aspect of larger
institutional change that is needed (31).

We have not been able to identify any other publications examining
scientific speaker diversity beyond gender. This seems to be the first.
This is concerning since conclusions drawn from gender-based studies are
often framed, and considered, to be applicable to other marginalized
groups (e.g., HURM). This is a flawed assumption. While there is no
doubt some overlap, each group remains marginalized due to a unique
complex set of factors that cannot always be solved by gender-based
solutions. US-serving institutions, such as the University of Michigan
have a particular responsibility to the historically suppressed
populations included in our definition of HURMs. We therefore implore US
institutions to apply this framing to their discussions and research.

According to social role theory, this department is not adequietly
serving their non-Caucasian trainees. Implict biases that affect
perceptions of marginalized groups are the primary issue, but we must
acknowledge that it is not always possible to identify members of
historically under-served communities. For instance, after data
analysis, we learned that at least one speaker in our data set should
have been categorized as a HURM instead of Caucasian, but it wasn't
readily apparent from their internet presence or CV. This limitation
makes two important points: that percieved identity often plays a larger
role than self-identification, and that we need better tools to identify
members of marginalized groups.

@@

In an attempt to promote inclusion within the Dept. M\&I these data were
presented to faculty members and the dept chair (Harry Mobley). Since,
trainee demographics were not represented within seminar speaker
demographics over the past 5 years, we proposed a policy change as to
how seminar speakers were being invited. This policy change included
switching from PI invited to lab invited in an attempt to allow trainees
to choose a speaker that best represented themselves. In addition to
this we also created resources which allowed scientists to self-identify
and provide host faculty with more diverse choices.

@@

To help address this issue, we make some suggestions (Table 1) and have
developed a resource to identify scientists who are members of
marginalized and/or historically under-served groups. Motivated by a
lack of such resources and inspired by similar resources--DiversifyEEB
and DiversifyChemistry--we created DiversifyMicrobiology and
DiversifyImmunology. These resources are a tool for symposium
organziers, award committees, search committees and other scientists to
identify individuals to diversify their pools. Additionally, we have
built these as a tool for use by other fields and organizations to
create their own lists. Importantly, since these lists are compiled by
self-nomination, we can ensure that only scientists comfortable
revealing their marginalized identities are included.

The self-nomination form is a Google Form with entries logged in a
private Google Sheet. This form is embedded within the website and can
be linked to directly. The use of a Google Forms allows us to maintain
this database at no cost and gives us the flexibility to add questions
or change response options without disrupting previous responses.
Entries are logged in a private spreadsheet so that entries can be
screened before being added to the public database. This screening
currently includes two steps: 1. Confirming that each person is listed
in the database only once. 2. Verifying that the submitted website is a
professional website for the person being listed. If a person has not
been listed in the database previously and passes step 2, a new entry is
added to the public database spreadsheet. If a person is already listed
in the database, their information is updated to the most recent
submission.

This public spreadsheet is embedded in the website and can be open
separately as a locked (uneditable) Google Sheet. Importantly, this
allows the list to be easily searched. We have chosen to list
individuals' academic information first in the spreadsheet to encourage
a focus on academic achievement rather than tokenization of marginalized
identities. Currently the database lists individuals in order of
self-nomination but future versions will be re-sorted based on name
and/or academic field to varying the individuals who may receive more
attention for simply being at the top of the list.

@@

A.K.H. collected the data, assigned demographics, analyzed the data, and
created the website. R.M.P. created the Google lists, forms, and website
content and the description of their maintenance. J.L. wrote the
introduction and provided conceptual advice. All authors contributed to
preparing the final manuscript.

@@

\hypertarget{ref-Hwang2008}{}
24. \textbf{Hwang W-C}, \textbf{Goto S}. 2008. The impact of perceived
racial discrimination on the mental health of asian american and latino
college students. Cultural Diversity and Ethnic Minority Psychology
\textbf{14}:326--335.
doi:\href{https://doi.org/10.1037/1099-9809.14.4.326}{10.1037/1099-9809.14.4.326}.

\hypertarget{ref-Tran2019}{}
25. \textbf{Tran VC}, \textbf{Lee J}, \textbf{Huang TJ}. 2019.
Revisiting the asian second-generation advantage. Ethnic and Racial
Studies \textbf{42}:2248--2269.
doi:\href{https://doi.org/10.1080/01419870.2019.1579920}{10.1080/01419870.2019.1579920}.

\hypertarget{ref-noauthor_seeking_2013}{}
26. 2013. Seeking Solutions: Maximizing American Talent by Advancing
Women of Color in Academia: Summary of a Conference. National Academies
Press, Washington, D.C.

\hypertarget{ref-whittaker_retention_2015}{}
27. \textbf{Whittaker JA}, \textbf{Montgomery BL}, \textbf{Martinez
Acosta VG}. 2015. Retention of Underrepresented Minority Faculty:
Strategic Initiatives for Institutional Value Proposition Based on
Perspectives from a Range of Academic Institutions. Journal of
undergraduate neuroscience education: JUNE: a publication of FUN,
Faculty for Undergraduate Neuroscience \textbf{13}:A136--145.

\hypertarget{ref-pololi_race_2010}{}
28. \textbf{Pololi L}, \textbf{Cooper LA}, \textbf{Carr P}. 2010. Race,
Disadvantage and Faculty Experiences in Academic Medicine. Journal of
General Internal Medicine \textbf{25}:1363--1369.
doi:\href{https://doi.org/10.1007/s11606-010-1478-7}{10.1007/s11606-010-1478-7}.

\hypertarget{ref-hassouneh_experiences_2014}{}
29. \textbf{Hassouneh D}, \textbf{Lutz KF}, \textbf{Beckett AK},
\textbf{Junkins EP}, \textbf{Horton LL}. 2014. The experiences of
underrepresented minority faculty in schools of medicine. Medical
Education Online \textbf{19}:24768.
doi:\href{https://doi.org/10.3402/meo.v19.24768}{10.3402/meo.v19.24768}.

\hypertarget{ref-Gibbs2016}{}
30. \textbf{Gibbs KD}, \textbf{Basson J}, \textbf{Xierali IM},
\textbf{Broniatowski DA}. 2016. Decoupling of the minority PhD talent
pool and assistant professor hiring in medical school basic science
departments in the US. eLife \textbf{5}.
doi:\href{https://doi.org/10.7554/elife.21393}{10.7554/elife.21393}.

\hypertarget{ref-johnson_msphere_2019}{}
31. \textbf{Johnson MDL}. 2019. mSphere of Influence: Hiring of
Underrepresented Minority Assistant Professors in Medical School Basic
Science Departments Has a Long Way To Go. mSphere \textbf{4}.
doi:\href{https://doi.org/10.1128/mSphere.00599-19}{10.1128/mSphere.00599-19}.

>>>>

\subsection{Conflicts of Interest}\label{conflicts-of-interest}

\vspace{40mm}

All authors affirm that there are no conflicts of interest.

@@

Social role theory emphasizes the importance of ``like'' representation
to improve feelings of self-efficacy and belonging. This is an issue for
trainees in the biological sciences who are either white women or
underrepresented minorities, since there is a lack of faculty who look
like them in biology academic settings. One way to improve
representation is through invited speaker series. In this persepective,
we compare the diversity of invited speakers at one microbiology and
immunology department to the diversity of their post-Baccalaurate
trainees. We find that trainees are not proportionally represented by
the invited speakers and provide policy suggestions and tools to address
this issue.

@@

Each academic year, each faculty member in the Department of
Microbiology and Immunology at the University of Michigan has the
opportunity to invite one speaker per year for a weekly seminar series.
Some of these seminar slots are dedicated to named lectureships, which
are decided by committee, and three trainee-invited speakers. We
analyzed the demographics of invited speakers and faculty hosts for five
academic years (Fall 2014 - Spring 2019), and compared them to the
current trainees when the data were analyzed (Spring 2019). Each speaker
was only counted once and those listed as departmental faculty members
or as a ``host'' at any point could not also be considered ``invited
speakers''. The list of faculty hosts was used as a proxy for faculty
demographics since as hosts, these faculty members are visible
representatives of the department. The trainees were identified using
from departmental email lists that included masters students, doctoral
students, and post-doctoral fellows.

This is a retrospective study, thus speakers were not asked for their
identities at the time of visit. Instead we hand-coded proxy
demographics using personal knowledge, photos, and CVs. The presenting
gender of each individual was assigned using a binary system
(man/woman). Due to the low number of individuals in the study,
race/ethnicity demographics were split in three groups: Caucasian,
Historically Under-represented Minority (HURM), and
Non-Caucasian/Non-HURM (NCNH), each with a binary (yes/no) possibilty.
Caucasian was assigned using the current U.S. Census definition where
those of Middle Eastern, European, and Russian descent are included.
HURM individuals were restricted to those with African-American,
Indigenous, Alaskan/Hawaian Native, Latinx and/or Hispanic heritage. All
others were placed into the NCNH group. We recognize that our proxy
demographics are a limitation of the analysis and want to acknowledge
that biological sex (male/female) is not always equivalent to the gender
that an individual presents as (man/woman), which is also distinct from
the gender(s) that an individual self-identifies as. We also want to
acknowledge that there are many other identities that are not captured
in this limited analysis.

@@

The more prestigous invited speaker lectureships were also dominated by
Caucasian scientists, who comprised 81.48\% of those awarded (Fig. 1C).
HURM and NCNH scientists were awarded 3 and 2 lectureships,
respectively. Because the intersection of identities can compound biases
and outcomes, we further examined the lectureships by gender and
race/ethnicity status. Caucasian men and women accounted for 44.44\% and
37.04\% of the lectureships, respectively. Just 18.52\% of lectureships
were held by non-Caucasian men while none were held by non-Caucasian
women (Fig. 1D).

@@

{[}Add paragraph summarizing findings {]} According to social role
theory, this department is not adequately serving their non-Caucasian
trainees.

Several papers have investigated the representation of women at
scientific conferences, however, we have only identified one that
focused on invited speakers at universities (23). In their study,
Nittrouer et al, examined 3,652 talks at 50 U.S. institutions in 2013 -
2014 and found that women faculty are less likely to be invited
speakers, despite similar acceptance rates. These results suggest that
women faculty are less often invited as speakers. We have not been able
to identify any other publications examining scientific speaker
diversity beyond gender. This seems to be the first. This is concerning
since conclusions drawn from gender-based studies are often framed, and
considered, to be applicable to other marginalized groups (e.g., HURM).
This is a flawed assumption. While there is no doubt some overlap, each
group remains marginalized due to a unique complex set of factors that
cannot always be solved by gender-based solutions. US-serving
institutions, such as the University of Michigan have a particular
responsibility to the historically suppressed populations included in
our definition of HURMs. We therefore implore US institutions to apply
this framing to their discussions and research.

Departments have different processes and criteria for selecting invited
speakers, but it is a matter of pride to bring the best scientists
possible. It may be that the definition of ``best'' poses a problem to
women, who need three-times as many publications as their men colleges
to be considered equally competent (24), and those that identify as HURM
and Asian, who report having to work harder than white men to be
perceived as legitimate scholars (25). Some departments only invite
tenured faculty, which severely limits the number of potential speakers
who are white women or non-Caucasian. Yet, another scenario is that
pre-tenure faculty members invite prestigious, tenured faculty in their
field to network and secure letters for their own tenure package. The
increased burden of white women and non-Caucasian scientists to prove
competency decreases their likelihood to be considered for either tenure
or as possible source of tenure letters.

Each underrepresented group in our cohort faces a complex set of
barriers to achieving faculty status. For instance, the decision to
invite a woman may also be negatively impacted by assumptions about
competency and dedication. The dedication of women who have children to
their work is perceived to be less than that of their colleagues, i.e.,
men who also have children (26--28). The perceived prioritization and
commitments of women to family over work may cause faculty to doubt
their acceptance of a speaking invitation, despite the prestigious
nature of these invitations and evidence that men and women accept at
similar rates ({\textbf{???}}, 23). As a result, the faculty member
invites a different colleague who they feel is more likely to agree (and
is a man). Another large portion of our sample were the NCNH cohort, who
are predominately Asian/Asian American individuals. Although Asian
scientists are well-represented in the US scientific workforce, they
face significant bias and barriers to inclusion in society and academia
(29, 30). For instance, despite the higher employment rate of Asian
scientists, they were not well-represented in the more prestigious
lectureships.

While HURM and NCNH share some experiences, differences including
varying rates of hiring and tenure promotion mean unique considerations
are important for inclusion of each group (31). For instance, a major
barrier to inclusion of HURM faculty at similar proportions to HURM
trainees is the low transition rate of scientists from HURM backgrounds
to faculty positions and the associated low proportion of HURM faculty
(32). The proportion of HURM faculty at the Assistant and Associate
Professor level is currently higher than at Full Professor so it will be
difficult to increase speaker diversity if early-career researchers are
not being considered (33). Increased performance expectations and
patterns of exclusions are consistent themes in studies characterizing
the HURM faculty experience (34, 35). Therefore, inclusion of HURM
faculty in seminar series is likely essential to increasing the number
of HURM Associate and Full Professors. Even when HURM speaker rates
match the proportion of HURM faculty employment, HURM trainees will be
represented at a significantly higher proportion. Inclusion of HURM
faculty in these seminarseries is just one aspect of larger
institutional change that is needed (36).

@@

In an attempt to promote inclusion within the Dept. M\&I these data were
presented to faculty members and the dept chair (Harry Mobley). Since,
trainee demographics were not represented within seminar speaker
demographics over the past 5 years, we proposed a policy change as to
how seminar speakers were being invited. This policy change included
switching from PI invited to lab invited in an attempt to allow trainees
to choose a speaker that best represented themselves.

Implict biases that affect perceptions of marginalized groups are the
primary issue, but we must acknowledge that it is not always possible to
identify members of historically under-served communities. For instance,
after data analysis, we learned that at least one speaker in our data
set should have been categorized as a HURM instead of Caucasian, but it
wasn't readily apparent from their internet presence or CV. This
limitation makes two important points: that percieved identity often
plays a larger role than self-identification, and that we need better
tools to identify members of marginalized groups. So in addition to our
policy change, we also created resources that allow scientists to
self-identify and provide host faculty with more diverse choices.

@@

To help address this issue, we make some suggestions (Table 1) and have
developed a resource to identify scientists who are members of
marginalized and/or historically under-served groups. Motivated by a
lack of such resources and inspired by similar resources--DiversifyEEB
and DiversifyChemistry--we created DiversifyMicrobiology and
DiversifyImmunology. These resources are a tool for symposium
organziers, award committees, search committees and other scientists to
identify individuals to diversify their pools. Additionally, we have
built these as a tool for use by other fields and organizations to
create their own lists. Since these lists are compiled by
self-nomination, we can ensure that only scientists comfortable
revealing their marginalized identities are included.

The self-nomination form is a Google Form with entries logged in a
private Google Sheet. This form is embedded within the website and can
be linked to directly. The use of a Google Forms allows us to maintain
this database at no cost and gives us the flexibility to add questions
or change response options without disrupting previous responses.
Entries are logged in a private spreadsheet so that entries can be
screened before being added to the public database. This screening
includes two steps: confirming that each person is listed in the
database only once and that any submitted website is a personal,
professional website. If both criteria are met, a new entry is added to
the public database spreadsheet. If a person is already listed in the
database, their information is updated to the most recent submission.

This public spreadsheet is embedded in the website and can be open
separately as a locked (uneditable) Google Sheet, allowing the list to
be easily searched. We have chosen to list individuals' academic
information first in the spreadsheet to encourage a focus on academic
achievement rather than tokenization of marginalized identities.
Currently the database lists individuals in order of self-nomination but
future versions will be re-sorted based on name and/or academic field to
varying the individuals who may receive more attention for simply being
at the top of the list.

@@

A.K.H. collected the data, assigned demographics, analyzed the data, and
created the website. R.M.P. created the Google lists, forms, and website
content and the description of their maintenance. J.L. wrote the
introduction and provided conceptual advice. A.K.H. and J.L facilited
the policy change to the UM Department of Microbiology and Immunology.
All authors contributed to preparing the final manuscript.

@@

\hypertarget{ref-BlairLoy2017}{}
24. \textbf{Blair-Loy M}, \textbf{Rogers L}, \textbf{Glaser D},
\textbf{Wong Y}, \textbf{Abraham D}, \textbf{Cosman P}. 2017. Gender in
engineering departments: Are there gender differences in interruptions
of academic job talks? Social Sciences \textbf{6}:29.
doi:\href{https://doi.org/10.3390/socsci6010029}{10.3390/socsci6010029}.

\hypertarget{ref-noauthor_seeking_2013}{}
25. 2013. Seeking Solutions: Maximizing American Talent by Advancing
Women of Color in Academia: Summary of a Conference. National Academies
Press, Washington, D.C.

\hypertarget{ref-Firth1982}{}
26. \textbf{Firth M}. 1982. Sex discrimination in job opportunities for
women. Sex Roles \textbf{8}:891--901.
doi:\href{https://doi.org/10.1007/bf00287858}{10.1007/bf00287858}.

\hypertarget{ref-Correll2007}{}
27. \textbf{Correll SJ}, \textbf{Benard S}, \textbf{Paik I}. 2007.
Getting a job: Is there a motherhood penalty? American Journal of
Sociology \textbf{112}:1297--1339.
doi:\href{https://doi.org/10.1086/511799}{10.1086/511799}.

\hypertarget{ref-Fuegen2004}{}
28. \textbf{Fuegen K}, \textbf{Biernat M}, \textbf{Haines E},
\textbf{Deaux K}. 2004. Mothers and fathers in the workplace: How gender
and parental status influence judgments of job-related competence.
Journal of Social Issues \textbf{60}:737--754.
doi:\href{https://doi.org/10.1111/j.0022-4537.2004.00383.x}{10.1111/j.0022-4537.2004.00383.x}.

\hypertarget{ref-Hwang2008}{}
29. \textbf{Hwang W-C}, \textbf{Goto S}. 2008. The impact of perceived
racial discrimination on the mental health of asian american and latino
college students. Cultural Diversity and Ethnic Minority Psychology
\textbf{14}:326--335.
doi:\href{https://doi.org/10.1037/1099-9809.14.4.326}{10.1037/1099-9809.14.4.326}.

\hypertarget{ref-Tran2019}{}
30. \textbf{Tran VC}, \textbf{Lee J}, \textbf{Huang TJ}. 2019.
Revisiting the asian second-generation advantage. Ethnic and Racial
Studies \textbf{42}:2248--2269.
doi:\href{https://doi.org/10.1080/01419870.2019.1579920}{10.1080/01419870.2019.1579920}.

\hypertarget{ref-Fang2000}{}
31. \textbf{Fang D}. 2000. Racial and ethnic disparities in faculty
promotion in academic medicine. JAMA \textbf{284}:1085.
doi:\href{https://doi.org/10.1001/jama.284.9.1085}{10.1001/jama.284.9.1085}.

\hypertarget{ref-Gibbs2016}{}
32. \textbf{Gibbs KD}, \textbf{Basson J}, \textbf{Xierali IM},
\textbf{Broniatowski DA}. 2016. Decoupling of the minority PhD talent
pool and assistant professor hiring in medical school basic science
departments in the US. eLife \textbf{5}.
doi:\href{https://doi.org/10.7554/elife.21393}{10.7554/elife.21393}.

\hypertarget{ref-whittaker_retention_2015}{}
33. \textbf{Whittaker JA}, \textbf{Montgomery BL}, \textbf{Martinez
Acosta VG}. 2015. Retention of Underrepresented Minority Faculty:
Strategic Initiatives for Institutional Value Proposition Based on
Perspectives from a Range of Academic Institutions. Journal of
undergraduate neuroscience education: JUNE: a publication of FUN,
Faculty for Undergraduate Neuroscience \textbf{13}:A136--145.

\hypertarget{ref-pololi_race_2010}{}
34. \textbf{Pololi L}, \textbf{Cooper LA}, \textbf{Carr P}. 2010. Race,
Disadvantage and Faculty Experiences in Academic Medicine. Journal of
General Internal Medicine \textbf{25}:1363--1369.
doi:\href{https://doi.org/10.1007/s11606-010-1478-7}{10.1007/s11606-010-1478-7}.

\hypertarget{ref-hassouneh_experiences_2014}{}
35. \textbf{Hassouneh D}, \textbf{Lutz KF}, \textbf{Beckett AK},
\textbf{Junkins EP}, \textbf{Horton LL}. 2014. The experiences of
underrepresented minority faculty in schools of medicine. Medical
Education Online \textbf{19}:24768.
doi:\href{https://doi.org/10.3402/meo.v19.24768}{10.3402/meo.v19.24768}.

\hypertarget{ref-johnson_msphere_2019}{}
36. \textbf{Johnson MDL}. 2019. mSphere of Influence: Hiring of
Underrepresented Minority Assistant Professors in Medical School Basic
Science Departments Has a Long Way To Go. mSphere \textbf{4}.
doi:\href{https://doi.org/10.1128/mSphere.00599-19}{10.1128/mSphere.00599-19}.
